---
title: "PhD Orthodontics: Content and Lead Generation Strategy"
subtitle: "AO3 Proposal Presentation"
author: "Xueying Luo"
institute: "MS Digital Marketing, Cal Poly Pomona"
date: today

format:
  revealjs:
    theme: serif
    width: 1600
    height: 900
    margin: 0.08
    footer: "PhD Orthodontics | Content & Lead Generation"
    transition: slide
    transition-speed: default
    incremental: false
    toc: true
    toc-depth: 1
    slide-number: c/t
    progress: true
    controls: true
    scrollable: true
    code-fold: false
    code-copy: true
    code-overflow: wrap
    number-sections: false
    embed-resources: true
    css: style.css

editor: visual

execute:
  echo: true
  warning: false
  message: false
  freeze: auto
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(gt)
```

# Introduction

## Project Background

- PhD Orthodontics is the client for our **MSDM Consulting Experience Project**.
- The full project covers website experience, SEO, content, paid search, and consumer insights.
- My focus is **AO3: Content and Lead Generation Strategy**.

::: {.fragment .fade-up}
> **AO3 asks:** Do prospective patients get the information they need to make a decision?
:::

::: notes
The broader consulting project contains five analytics objectives. My part is AO3. The purpose of this presentation is to explain what AO3 evaluates, how it differs from the other objectives, and how I plan to conduct the content-gap analysis.
:::

## Where AO3 Fits

Each analytics objective addresses a different question in the prospective-patient journey.

| AO | Core Question |
|------------------------------------|------------------------------------|
| **AO1** | Can users move through the website easily and reach a consultation? |
| **AO2** | Can prospective patients find the practice through search? |
| **AO3** | Do prospective patients get the information they need to make a decision? |
| **AO4** | Which paid-search patterns generate more efficient qualified inquiries? |
| **AO5** | Why do certain messages influence trust and consultation intention? |

::: callout-note
## AO3 Boundary

AO3 focuses on **what information the website provides**, rather than usability, SEO visibility, paid-search efficiency, or experimental consumer-response effects.
:::

::: notes
This distinction is important because the project has five related objectives. AO1 focuses on usability, AO2 on discoverability, AO3 on content, AO4 on paid-search efficiency, and AO5 on consumer response.
:::

## Business Problem

Prospective patients may use an orthodontic website to understand treatments, evaluate the provider, and decide whether to request a consultation.

> **Does the website provide enough clear, complete, credible, and decision-relevant information for prospective patients to make an informed next-step decision?**

A content gap may exist when important information is:

::: incremental
- missing,
- unclear,
- incomplete, or
- not useful enough for decision-making.
:::

## Analytics Objective 3

> **AO3:** Do prospective patients get the information they need to make a decision?

The analysis will examine:

::: incremental
- content coverage,
- clarity,
- completeness,
- credibility, and
- decision relevance.
:::

The goal is to determine which information should be **improved, clarified, expanded, or created** to better support consultation decisions.

::: notes
The current direction follows Professor Xie's feedback to narrow the scope and make Structured Content Gap Analysis the primary analytical approach.
:::

## Current Scope

::::: columns
::: {.column width="50%"}
### AO3 Will Evaluate

- information provided on the website
- patient information needs
- content completeness
- content clarity
- decision-relevant gaps
:::

::: {.column width="50%"}
### AO3 Will Not Lead

- navigation or usability
- SEO ranking performance
- paid-ad efficiency
- experimental persuasion effects
:::
:::::

**San Gabriel is the primary current focus.**

## Why AO3 Matters

Website content can help prospective patients do two important things.

::::: columns
::: {.column width="50%"}
### Understand the Treatment

- available treatment options
- treatment process
- risks and limitations
- retention and follow-up
- cost and payment considerations
:::

::: {.column width="50%"}
### Evaluate the Practice

- provider experience and expertise
- treatment alternatives
- credibility of information
- fit with patient needs
- whether to request a consultation
:::
:::::

::: {.fragment .fade-up}
**The goal is not simply to add more content. It is to provide the right information in a useful form.**
:::

# Literature Review

## Evidence for Content Gaps

Previous orthodontic research suggests that online information can have important quality and readability limitations.

::: incremental
- **Meade, Poirier, and Jensen (2024):** online orthodontic information was often low to moderate in quality and difficult to read.
- **Meade and Dreyer (2022):** dental-practice websites showed information-quality and readability problems.
- **Ferlias et al. (2023):** U.S. orthodontic websites showed gaps in areas such as relapse-risk and retention information.
:::

::: {.fragment .fade-up}
> Having a treatment page does not necessarily mean the information is **complete, understandable, or useful for decision-making**.
:::

## Supporting Evidence

The content-gap analysis will also draw on research about:

::::: columns
::: {.column width="50%"}
- orthodontic information quality
- readability
- provider-selection factors
:::

::: {.column width="50%"}
- credibility
- uncertainty reduction
- decision-support information
:::
:::::

Provider-selection research suggests that patients may consider:

- experience and reputation,
- treatment explanations,
- treatment quality,
- cost and payment, and
- convenience.

::: callout-note
## Role of Theory

Theory helps explain **why certain information may matter**, but it does not organize AO3.

**Primary analytical approach: Structured Content Gap Analysis**
:::

::: notes
Earlier versions included several theories as separate frameworks. Based on faculty feedback, those theories now serve only as supporting literature. ELM is more appropriate for AO5.
:::

## Adequacy of Existing Information

Existing evidence helps identify **what types of information should be examined**, but it does not reveal PhD Orthodontics' specific content priorities by itself.

Current evidence includes:

::: incremental
- orthodontic information-quality and readability research,
- provider-selection research,
- the current PhD Orthodontics website,
- competitor orthodontic websites,
- Google and Yelp patient reviews, and
- common orthodontic search themes.
:::

::: {.fragment .fade-up}
The actual content gaps must be identified through the project analysis.
:::

## What We Still Need to Learn

::::: columns
::: {.column width="50%"}
### Team Will Generate

- website content audit
- competitor comparison
- review-theme analysis
- search-theme analysis
- content-gap identification
- content prioritization
:::

::: {.column width="50%"}
### Client Needs to Confirm

- priority treatments/services
- key differentiators
- outdated information
- restrictions on claims
- available inquiry data
- future Chino Hills needs
:::
:::::

::: notes
This follows the faculty feedback to separate information the research team can generate from information that needs to come directly from the client.
:::

# Methods

## Primary Analytical Approach

### Structured Content Gap Analysis

AO3 will compare the current website with several evidence sources to identify information that is **missing, weak, unclear, inconsistent, or insufficient**.

```{mermaid}
flowchart LR
    A[Current Website] --> E[Content Gap Analysis]
    B[Competitors] --> E
    C[Reviews + Search Themes] --> E
    D[Supporting Literature] --> E
    E --> F[Prioritized Content Opportunities]
```

::: notes
Competitor websites are benchmarks, not automatically examples of best practice. The goal is to use multiple sources together rather than copy what competitors do.
:::

## Data Sources

::::: columns
::: {.column width="50%"}
### Primary Sources

- PhD Orthodontics website
- competitor websites
- Google/Yelp reviews
- common orthodontic search themes
:::

::: {.column width="50%"}
### Supporting Sources

- academic literature
- GA4 data
- Google Search Console
- aggregate inquiry information
:::
:::::

::: aside
Behavioral metrics can support interpretation, but engagement alone does not prove content quality.
:::

## Data Preparation

The collected information will be organized into a consistent structure before comparison.

::::::::::::: columns
:::: {.column width="20%"}
::: process-step
**1. Inventory**

List major pages.
:::
::::

:::: {.column width="20%"}
::: process-step
**2. Classify**

Group content types.
:::
::::

:::: {.column width="20%"}
::: process-step
**3. Organize**

Structure reviews and search themes.
:::
::::

:::: {.column width="20%"}
::: process-step
**4. Standardize**

Use shared audit categories.
:::
::::

:::: {.column width="20%"}
::: process-step
**5. Analyze**

Compare and prioritize gaps.
:::
::::
:::::::::::::

::: notes
This creates a consistent dataset so that website pages, competitors, reviews, search themes, and research can be compared more systematically.
:::

## Content Audit Measures

Each selected page can be evaluated using a consistent set of criteria.

| Criterion | Main Question |
|------------------------------------|------------------------------------|
| **Completeness** | Does the page address important patient questions? |
| **Clarity** | Is the information understandable? |
| **Credibility** | Are claims and provider information sufficiently supported? |
| **Decision relevance** | Does the content help patients evaluate treatment or the practice? |
| **Risks / alternatives** | Are important risks, limits, or alternatives addressed? |
| **Cost / payment** | Is financial information available where expected? |
| **Retention / follow-up** | Are longer-term expectations explained where relevant? |

::: notes
The criteria can be refined as research progresses. Their purpose is to translate prior research and patient-information needs into practical audit measures.
:::

## Analysis Process

::: incremental
### 1. Inventory

Identify major website pages and content areas.

### 2. Evaluate

Code each page using the content-audit criteria.

### 3. Compare

Compare PhD Orthodontics with competitors, patient-review themes, search themes, and supporting literature.

### 4. Prioritize

Rank gaps using patient relevance, business relevance, supporting evidence, and decision value.
:::

# Reproducible Analysis

## Reproducible Content Audit: Code

The audit structure can be created directly in R.

```{r}
#| label: create-content-audit
#| echo: true
#| output: false

content_audit <- tibble(
  content_area = c(
    "Treatment overview",
    "Treatment suitability",
    "Risks and limitations",
    "Cost and payment",
    "Retention and follow-up"
  ),
  website = rep("To audit", 5),
  competitor_comparison = rep("Pending", 5),
  review_search_evidence = rep("Pending", 5)
)
```

::: callout-tip
Because the audit is created from code, it can be updated later without rebuilding the presentation table manually.
:::

## Reproducible Content Audit: Output

```{r}
#| label: tbl-content-audit
#| tbl-cap: "Illustrative Content-Audit Structure"
#| echo: false

content_audit |>
  gt() |>
  cols_label(
    content_area = "Content Area",
    website = "PhD Website",
    competitor_comparison = "Competitor Review",
    review_search_evidence = "Reviews / Search Themes"
  ) |>
  tab_header(
    title = "AO3 Content-Audit Template",
    subtitle = "Illustrative structure for the planned analysis"
  ) |>
  tab_options(
    table.font.size = px(22),
    heading.title.font.size = px(26),
    heading.subtitle.font.size = px(19)
  )
```

The current values are placeholders because the full content audit has not yet been completed.

::: notes
This is an illustrative framework rather than a claim about current client performance. Actual findings will replace the placeholder values as the analysis progresses.
:::

# Expected Output

## Prioritizing Content Opportunities

The final AO3 analysis should produce a **prioritized set of content recommendations**.

::: incremental
- strengthen existing treatment pages,
- create or expand FAQs,
- clarify risks, limitations, and alternatives,
- improve cost and payment information,
- strengthen provider-expertise information,
- improve retention and follow-up content,
- develop educational resources, and
- identify future location-specific content needs.
:::

::: {.fragment .fade-up}
Recommendations will be based on **multiple evidence sources**, rather than competitor imitation or individual reviews alone.
:::

# Key Takeaways

::: callout-important
## Primary Approach

**Structured Content Gap Analysis**
:::

::: incremental
- AO3 focuses on **what information prospective patients receive**.
- Evidence will come from the website, competitors, reviews, search themes, and research.
- Supporting theory helps explain why information matters, but does not organize the analysis.
- The project separates evidence the **team can generate** from information the **client must confirm**.
- The final output will be a **prioritized set of actionable content recommendations**.
:::

# References

## Key Sources

::: small
- Meade, Poirier, and Jensen (2024). Research examining the quality and readability of online orthodontic information.
- Meade and Dreyer (2022). Research examining information quality and readability on dental-practice websites providing orthodontic information.
- Ferlias et al. (2023). Research examining information quality and content gaps on U.S. orthodontic websites.
- Fatah et al. (2021). Research examining factors involved in orthodontic provider selection.
- Olson et al. (2020). Research examining patient preferences and provider-selection factors.
:::

::: callout-note
The final project report will use the team's required **AMA citation style** consistently.
:::

# Appendix

## Publication Links

- [**GitHub Repository**](https://github.com/Sheilaaa0312/PhD-Orthodontics-AO3-Revealjs)
- [**Published Revealjs Presentation**](https://sheilaaa0312.github.io/PhD-Orthodontics-AO3-Revealjs/#/title-slide)
