---
title: "PhD Orthodontics: Content and Lead Generation Strategy"
subtitle: "AO3 Proposal Presentation"
author: "Xueying Luo"
institute: "MS Digital Marketing, Cal Poly Pomona"
date: today

format:
  revealjs:
    theme: serif
    width: 1600
    height: 900
    margin: 0.08
    footer: "PhD Orthodontics | Content & Lead Generation"
    transition: slide
    transition-speed: default
    incremental: false
    toc: true
    toc-depth: 1
    slide-number: c/t
    progress: true
    controls: true
    scrollable: true
    code-fold: false
    code-copy: true
    code-overflow: wrap
    number-sections: false
    embed-resources: true
    css: style.css

editor: visual

execute:
  echo: true
  warning: false
  message: false
  freeze: auto
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(gt)
```

# Introduction

## Project Background

- PhD Orthodontics is the client for our **MSDM Consulting Experience Project**.
- The full project covers website experience, SEO, content, paid search, and consumer insights.
- My focus is **AO3: Content and Lead Generation Strategy**.

::: {.fragment .fade-up}
> **AO3 asks:** Do prospective patients get the information they need to make a decision?
:::

::: notes
This is the audience-friendly version of AO3. The formal objective is to identify and prioritize gaps between information prospective patients may need before contacting PhD Orthodontics and the information currently provided on the website.
:::

## Where AO3 Fits

Each analytics objective addresses a different question in the prospective-patient journey.

| AO | Core Question |
|----|----|
| **AO1** | Can users move through the website easily and reach a consultation? |
| **AO2** | Can prospective patients find the practice through search? |
| **AO3** | Do prospective patients get the information they need to make a decision? |
| **AO4** | Which paid-search patterns generate more efficient qualified inquiries? |
| **AO5** | Why do certain messages influence trust and consultation intention? |

::: callout-note
## AO3 Boundary

AO3 focuses on **what information the website provides**, rather than usability, SEO visibility, paid-search efficiency, or experimental consumer-response effects.
:::

## Business Problem

Prospective patients may use an orthodontic website to understand treatments, evaluate the provider, and decide whether to contact the practice.

> **Does the current website provide the information prospective patients may need to understand treatment options and make a decision before contacting PhD Orthodontics?**

A content gap may involve information that is:

::: incremental
- missing,
- incomplete,
- unclear,
- inconsistent,
- difficult to locate, or
- not detailed enough to answer an important patient question.
:::

## Analytics Objective 3

### Formal AO3

> **Identify and prioritize gaps between the information prospective patients may need to understand treatment options and make a decision before contacting PhD Orthodontics and the information currently provided on the website.**

### Plain-Language Question

> **Do prospective patients get the information they need to make a decision?**

## What AO3 Will Evaluate

The content audit will examine six main criteria:

::: incremental
1.  **Presence of important information**
2.  **Completeness and depth**
3.  **Clarity and readability**
4.  **Accuracy and reliability**
5.  **Consistency across related pages**
6.  **Balance of relevant treatment information**
:::

The goal is to determine which information should be **clarified, expanded, updated, or created**.

## Current Scope

::::: columns
::: {.column width="50%"}
### AO3 Will Evaluate

- website information
- patient information needs
- missing or incomplete content
- clarity and readability
- consistency and reliability
- balanced treatment information
:::

::: {.column width="50%"}
### AO3 Will Not Lead

- website navigation or usability
- SEO ranking performance
- paid-search efficiency
- experimental persuasion effects
:::
:::::

**San Gabriel is the primary current focus; Chino Hills is treated as a future location-specific content opportunity as planning develops.**

## Why AO3 Matters

Website content can help prospective patients do two important things.

::::: columns
::: {.column width="50%"}
### Understand Treatment

- suitability
- process and duration
- benefits and limitations
- risks and alternatives
- retention and follow-up
- cost or insurance
:::

::: {.column width="50%"}
### Evaluate the Practice

- provider qualifications
- treatment explanations
- reliability of information
- consistency across pages
- fit with patient needs
- whether to contact the practice
:::
:::::

::: {.fragment .fade-up}
**The goal is not simply to add more content. It is to provide the right information clearly and sufficiently.**
:::

# Literature Review

## Evidence for Content Gaps

Previous orthodontic research suggests that online information may have quality and readability limitations.

::: incremental
- **Meade, Poirier, and Jensen (2024):** online orthodontic information was often low to moderate in quality and difficult to read.
- **Meade and Dreyer (2022):** dental-practice websites showed information-quality and readability problems.
- **Ferlias et al. (2023):** U.S. orthodontic websites showed gaps in areas such as relapse-risk and retention information.
:::

::: {.fragment .fade-up}
> Having information on a page does not necessarily mean that it is **complete, understandable, reliable, consistent, or sufficiently balanced**.
:::

## Supporting Evidence

The Content Gap Analysis will be supported by research on:

::::: columns
::: {.column width="50%"}
- information quality
- readability
- treatment risks
- retention and follow-up
:::

::: {.column width="50%"}
- provider-selection factors
- reliability and credibility
- treatment alternatives
- patient information needs
:::
:::::

::: callout-note
## Role of Theory

Supporting concepts such as signaling and credibility can help explain **why certain information may matter**, but they do not organize AO3.

**Primary analytical framework: Content Gap Analysis**
:::

::: notes
Earlier versions of AO3 included several theoretical models. Based on faculty feedback, the scope was simplified. ELM fits better with AO5, while AO3 is now organized around Content Gap Analysis.
:::

## Adequacy of Existing Information

Existing evidence is adequate for defining **what should be examined**, but it cannot determine the specific content priorities for PhD Orthodontics by itself.

Current evidence includes:

::: incremental
- orthodontic information-quality and readability research,
- provider-selection research,
- the current PhD Orthodontics website,
- selected competitor websites,
- Google and Yelp patient reviews, and
- common orthodontic search themes.
:::

Competitor sites and reviews provide useful comparison evidence, but they should not automatically be treated as best practice or as representative of all prospective patients.

## What We Still Need

::::: columns
::: {.column width="50%"}
### Team Will Generate

- structured website content audit
- competitor comparison
- Google/Yelp review-theme analysis
- common search-theme analysis
- identification of content gaps
- prioritization of content opportunities
:::

::: {.column width="50%"}
### Client Needs to Confirm

- priority services
- key PhD Orthodontics differentiators
- outdated website content
- future Chino Hills plans
:::
:::::

::: notes
This distinction follows faculty feedback to separate information that can be generated through research from information that must be confirmed by the client.
:::

# Methods

## Primary Analytical Approach

### Structured Content Gap Analysis

The basic analytical process is:

**Patient information need → Current website content → Gap or weakness → Priority → Content recommendation**

```{mermaid}
flowchart LR
    A[Patient Information Needs] --> E[Content Gap Analysis]
    B[Current Website] --> E
    C[Competitors + Reviews] --> E
    D[Search Themes + Research] --> E
    E --> F[Gap or Weakness]
    F --> G[Priority]
    G --> H[Content Recommendation]
```

::: notes
Competitor websites are benchmarks rather than automatic examples of best practice. The analysis will rely on patterns across several sources.
:::

## Data Sources

::::: columns
::: {.column width="50%"}
### Core Evidence

- PhD Orthodontics website
- selected competitor websites
- Google/Yelp reviews
- common orthodontic search themes
- relevant orthodontic research
:::

::: {.column width="50%"}
### Supporting Performance Data

- GA4, where available
- Google Search Console
- validated aggregate consultation-inquiry data
:::
:::::

::: callout-note
## Role of Performance Data

GA4, Google Search Console, and validated aggregate inquiry data may help **prioritize pages or topics**, but they will **not** be treated as direct measures of content quality or patient information needs.
:::

## Data Preparation

The collected information will be organized into a consistent structure before comparison.

::::::::::::: columns
:::: {.column width="20%"}
::: process-step
**1. Inventory**

List major pages.
:::
::::

:::: {.column width="20%"}
::: process-step
**2. Classify**

Group content topics.
:::
::::

:::: {.column width="20%"}
::: process-step
**3. Code**

Apply audit criteria.
:::
::::

:::: {.column width="20%"}
::: process-step
**4. Compare**

Review evidence sources.
:::
::::

:::: {.column width="20%"}
::: process-step
**5. Prioritize**

Rank content gaps.
:::
::::
:::::::::::::

## Content Audit Measures

Each selected page will be coded using a consistent set of criteria.

| Criterion | Main Question |
|----|----|
| **Presence** | Is important information provided? |
| **Completeness / depth** | Is enough detail provided to answer an important patient question? |
| **Clarity / readability** | Is the information understandable to a prospective patient? |
| **Accuracy / reliability** | Is the information appropriately supported and reliable? |
| **Consistency** | Is related information consistent across website pages? |
| **Balance** | Are relevant benefits, limitations, risks, or alternatives presented where appropriate? |

Possible content topics include treatment suitability, process and duration, benefits and limitations, risks and alternatives, retention or follow-up, cost or insurance, and provider qualifications.

## Analysis Process

::: incremental
### 1. Inventory

Identify major website pages and content areas.

### 2. Evaluate

Code pages for presence, completeness/depth, clarity/readability, accuracy/reliability, consistency, and balance.

### 3. Compare

Compare the website with patient-review themes, competitor content, common search themes, and supporting literature.

### 4. Identify Gaps

Identify information that is missing, incomplete, unclear, inconsistent, difficult to locate, or insufficiently developed.

### 5. Prioritize

Rank gaps using recurring evidence across sources, prospective-patient relevance, supporting research, and business relevance.
:::

# Reproducible Analysis

## Content-Area Tracking: Code

The following R code creates an illustrative structure for organizing evidence during the planned content-gap analysis.

```{r}
#| label: create-content-audit
#| echo: true
#| output: false

content_audit <- tibble(
  content_area = c(
    "Treatment suitability",
    "Process and duration",
    "Risks and alternatives",
    "Cost and insurance",
    "Retention and follow-up"
  ),
  phd_website = rep("To audit", 5),
  competitor_evidence = rep("Pending", 5),
  review_search_evidence = rep("Pending", 5)
)
```

::: callout-tip
Because the table is generated from R code, the values can be updated later without rebuilding the presentation manually.
:::

## Content-Area Tracking: Output

```{r}
#| label: tbl-content-audit
#| tbl-cap: "Illustrative Content-Area Tracking Structure"
#| echo: false

content_audit |>
  gt() |>
  cols_label(
    content_area = "Content Area",
    phd_website = "PhD Website",
    competitor_evidence = "Competitor Evidence",
    review_search_evidence = "Reviews / Search Themes"
  ) |>
  tab_header(
    title = "AO3 Content-Area Tracking Template",
    subtitle = "Illustrative structure for organizing planned content-gap evidence"
  ) |>
  tab_options(
    table.font.size = px(22),
    heading.title.font.size = px(26),
    heading.subtitle.font.size = px(19)
  )
```

The current values are placeholders because the full content audit has not yet been completed.

::: notes
This table illustrates how evidence can be organized. It does not claim that these areas are already confirmed problems for PhD Orthodontics.
:::

# Expected Output

## Prioritizing Content Opportunities

The final analysis should identify two broad types of opportunities:

::::: columns
::: {.column width="50%"}
### Improve Existing Content

- clarify unclear information
- expand incomplete explanations
- improve consistency
- strengthen support or balance
- update outdated information
:::

::: {.column width="50%"}
### Create New Content

- service pages
- educational resources
- FAQs
- location-specific pages
- landing pages
:::
:::::

Recommendations will be prioritized using **patterns across multiple sources**, rather than any single competitor, review, or study.

# Key Takeaways

::: callout-important
## AO3 Direction

**Primary analytical framework: Content Gap Analysis**
:::

::: incremental
- AO3 asks whether prospective patients receive the information they need before contacting the practice.
- Website content will be coded using six consistent audit criteria.
- Competitors, reviews, search themes, and orthodontic research will provide comparison evidence.
- Performance data may support prioritization but will not measure content quality directly.
- San Gabriel is the current focus; Chino Hills is a future content opportunity.
- The final output will be prioritized recommendations for improving existing content or creating new content.
:::

# References

## Key Sources

::: small
- Meade, Poirier, and Jensen (2024). Research on the quality and readability of Web-based orthodontic information.
- Meade and Dreyer (2022). Research on the quality and readability of orthodontic information on dental-practice websites.
- Ferlias et al. (2023). Research examining orthodontic website information, including relapse-risk and retention content.
- Fatah et al. (2021). Research related to factors involved in orthodontic provider selection.
- Olson et al. (2020). Research related to patient preferences and provider-selection factors.
:::

::: callout-note
The group CEP report uses the shared bibliography and the team's required citation style. These sources are shown here in shortened presentation format.
:::

# Appendix

## Publication Links

- [**GitHub Repository**](https://github.com/Sheilaaa0312/PhD-Orthodontics-AO3-Revealjs)
- [**Published Revealjs Presentation**](https://sheilaaa0312.github.io/PhD-Orthodontics-AO3-Revealjs/#/title-slide)
